The electronic structure of aqueous KCl revealed by X-ray absorption and Auger electron spectroscopy \\ The all-seeing eye of Auger electron spectroscopy: a study on aqueous KCl

### 2018-01-09 abstract.tex
Kolya's changes (Jan 9)
Auger figure, author list

X-ray absorption and Auger electron spectroscopies are powerful tools to probe the electronic structure and immediate surroundings of ions in a solution. In this work we use a combination of these spectroscopies to study the electronic structure and decay of aqueous KCl at the K-edges of \ki~and \cli. Although the two ions are isoelectronic, their Auger electron spectra as a function of the photon energy exhibit notably different features. To explain these differences, we carried out {\it ab initio} calculations of both the core excited states and the final Auger states of \ki, \cli~and their microsolvated clusters. Our calculations show that the energy order of the 3d and 4p orbitals is inverted in \ki~with respect to \cli. The reverse orbital order in the two ions is reflected in both the ordering of the core excited states and in the final states populated in the resonant Auger decay. Furthermore, the energetic proximity of the 3d and 4p virtual states in the bare \ki~ion leads to their mixing in the presence of the solvent, and to the population of the dipole forbidden 1s$\,\rightarrow\,$3d state upon K-shell excitation in an aqueous solution. The resonant Auger decay of this state results in a separate feature in the Auger electron spectrum of \ki~which is absent in the spectrum of \cli.

>>>>

%Kolya and Nico corrected Jan 8
X-ray absorption and Auger electron spectroscopies are powerful tools to probe the electronic structure and immediate surroundings of ions in a solution. In this work we use a combination of these spectroscopies to study the electronic structure and decay in aqueous KCl at the K-edges of \ki~and \cli. Although the two ions are isoelectronic, their Auger electron spectra as a function of the photon energy exhibit notably different features. To explain these differences, we carried out {\it ab initio} calculations of both the core excited states and the final Auger states of \ki, \cli~and their microsolvated clusters. Our calculations show that the energy order of the 3d and 4p orbitals is inverted in \ki~with respect to \cli. The reverse orbital order in the two ions is reflected in both the ordering of the core excited states and in the final states populated in the resonant Auger decay. The energetic proximity of the 3d and 4p virtual states in the bare \ki~ion leads to their mixing in the presence of the solvent, and to the population of the dipole forbidden 1s$\,\rightarrow\,$3d state upon K-shell excitation in an aqueous solution. The resonant Auger decay of this state results in a separate feature in the Auger electron spectrum of \ki~which is absent in the spectrum of \cli.

### 2018-01-09 introduction.tex
Kolya's changes (Jan 9)
Auger figure, author list

X-ray absorption and Auger electron spectroscopies are powerful tools to study the electronic structure and the nearest environment of atoms and molecules in gas, liquid and solid phase. Understanding how atoms or molecules respond to irradiation with x-rays gives insight into the structure of solutions \citep{Pokapanich09:7264}, and the mechanism of radiation damage \citep{ONeill02:329,Carugo05:213,Stumpf16:237}. Upon absorption of an x-ray photon, core excited or core ionized states of a specific atom are populated depending on the photon energy. The relaxation of these highly energetic states involves an ultrafast cascade of intraatomic processes, such as radiative and Auger decay. Furthermore, if the initially excited or ionized species is embedded in an environment, interatomic processes such as interatomic Coulombic decay (ICD) and related processes \citep{Pokapanich09:7264,Pokapanich11:13430,Stumpf16:237,unger17:708} are possible.

>>>>

X-ray absorption and Auger electron spectroscopies are powerful tools to study the electronic structure and the nearest environment of atoms and molecules in gas, liquid and solid phase. Understanding how atoms or molecules respond to irradiation with x-rays gives insight into the structure of solutions \citep{nagasaka14:4388}, and the mechanism of radiation damage \citep{ONeill02:329,Carugo05:213,Stumpf16:237}. Upon absorption of an x-ray photon, core excited or core ionized states of a specific atom are populated depending on the photon energy. The relaxation of these highly energetic states involves an ultrafast cascade of intraatomic processes, such as radiative and Auger decay. Furthermore, if the initially excited or ionized species is embedded in an environment, interatomic processes such as interatomic Coulombic decay (ICD) and related processes \citep{Pokapanich09:7264,Pokapanich11:13430,Stumpf16:237,unger17:708} are possible.
